Operation Manual

### 2024-10-22 docs/writing/outline.tex
Edits to outline and gitignore

	\item Tina is open source and able to be assembled with 3D printed parts, OpenBuilds parts kits, and hand tools

@@

		\item **Lizzie add here**

@@

		\item understanding tree growth mechanisms

@@

@@

\item Results
	\begin{enumerate}
	\item scans of cookies / cores
		\begin{enumerate}
		\item ultra high resolution scans (DPI 15,000 +)
		\item downscaled versions as high resolution is not necessary for all applications
		\item Digitization time as a function of surface area. Large cookies can scan only a portion of the cookie including the center and half of the rings.
		\item large surface areas can produce files that are inconveniently large
		\end{enumerate}
	\item File-size results in functional limits 
		\begin{enumerate}
		\item max filesize for TIFF files is 2.5 GB
		\item other lossless filetypes for larger images are not compatible with standard image viewers
		\item workaround with NumPy memory maps and cropped viewing 
		\end{enumerate}
	\end{enumerate}
\item Discussion (for MEE Only)
	\begin{enumerate}
	\item strengths and opportunities
		\begin{enumerate}
		\item  Ability to capture multiple cores / cookies simultaneously
		\item cost effective
		\item potential for automatic tree ring identification with iamge processing / ML 
		\item potential for vessel counts for an entire ring 
		\subitem although final quality is only as good as the sample preparation
		\end{enumerate}
	\item opportunities for improvements
		\begin{enumerate}
		\item focus stacking
			\begin {enumerate}
			\item when a sample is microtomed, the vessels are hollow. The autofocusing algorithm can be confused from this 
			\end{enumerate}
			\item Lenses
			\begin{enumerate}
				\item troubles with fixed aperature / non autofocusing / poorly manufactured lens
				\item lack of control to increase sharpness
				\item autofocusing with Z-axis movement is time consuming to do without image blur
				\item poor lens manufacturing can lead to drastically different quality / lighting between the edges and center of an image
				\item good lens can increase sharpness and therefore stitching accuracy and ML inference
				\item obtain similar quality between the corner and center of the image
				\item Difficulty stitching with lower detail images, can't increase digitizing speed, must downscale high resolution images 
				\end{enumerate}
		\end{enumerate}
		\begin{enumerate}
		\item poor lens quality seemed to be the culprit of producing visible seams when stitching with larger field of view images 
		\end{enumerate}
	\item tested on R-CNN
		\begin{enumerate}
		\item Cookie with a dpi of SMALL and dpi of 13500 were tested. With total pixel count of SMALL and BIG
			\begin{enumerate}
			\item NEEDS specific: DPI, height and width of pixels, record runtime
			\item NEEDS specifications of server computational power (GPU count/other metric for ANN power)
			\end{enumerate}
		\end{enumerate}
	\item tested on CooRecorder + CDendro
		\begin{enumerate}
		\item Maximum filesize 
		\item Coordinates were registered on to the cookie scans 
		\item Note to self: using CDendro for multiple samples from the same tree... (cookies) 
		\end{enumerate}
	\item Software support for large files 
		\begin{enumerate}
		\item Not all software can support this, especially if the computer is RAM constrained. Ring analysis tool which uses BigTIFF, HD5, or memory maps and loads only partial portions of the full image would be useful
		\end{enumerate}
	\end{enumerate}
\item Conclusions (optional for MEE)
	\begin{enumerate}
	\item empty
	\end{enumerate}

>>>>

	\item Tina is open source and able to be assembled with 3D printed parts, OpenBuilds parts kits, and hand tools % Can we add how much ours costs?

@@

		\item tree rings provide critical data/insights across multiple fields

@@

		\item understanding tree growth mechanisms (plant bio/ecology)
	% Consider adding this to below points (Development of scanning alternatives) as one paragraph on its own
	\item Getting these data means measuring tree rings -- quick history
		\item originally done on scopes
		\item images important for several decades now (WinDendro?) 
		\item But new methods coming up often to take advantage of better imaging technology ... 
		% \item Could add here one sentence on the three methods you mention below depending on what you want to say ... 

@@

	% I suggest a more 'here we ....' paragraph next that includes the below points so something like: (comment this in if you like it and delete your section below
	\iffalse
	\item Here we tell you about our new device
		\item We review hardware and software % Could add total estimated cost?
		\item Then show how the method can be used to record annual growth through current common programs pr ...
	\fi

@@

\item Results
	\item scans of cookies / cores
		\item ultra high resolution scans (DPI 15,000 +)
		\item downscaled versions as high resolution is not necessary for all applications
		\item Digitization time as a function of surface area. Large cookies can scan only a portion of the cookie including the center and half of the rings.
		\item large surface areas can produce files that are inconveniently large
	\item File-size results in functional limits 
		\item max filesize for TIFF files is 2.5 GB
		\item other lossless filetypes for larger images are not compatible with standard image viewers
		\item workaround with NumPy memory maps and cropped viewing 
\item Discussion (for MEE Only) 
	\item strengths and opportunities
		\begin{enumerate} % Usually I like a quick overview paragraph and I think you should still have one but as currently written I think the 'potential for automatic tree ring identification with iamge processing / ML ' and 'potential for vessel counts for an entire ring' connect too much to later sections, so you should move those sections up 
		\item  Ability to capture multiple cores / cookies simultaneously
		\item cost effective
		% I would move the section on  tested on CooRecorder + CDendro here then 
		% Section on R-CNN here then ... a paragraph on potential for two things below (or you could have these points on potential as part of your conclusions)
		\item potential for automatic tree ring identification with iamge processing / ML 
		\item potential for vessel counts for an entire ring 
		\subitem although final quality is only as good as the sample preparation
	\item opportunities for improvements
		\item focus stacking
			\begin {enumerate}
			\item when a sample is microtomed, the vessels are hollow. The autofocusing algorithm can be confused from this 
			\item Lenses
				\item troubles with fixed aperature / non autofocusing / poorly manufactured lens
				\item lack of control to increase sharpness
				\item autofocusing with Z-axis movement is time consuming to do without image blur
				\item poor lens manufacturing can lead to drastically different quality / lighting between the edges and center of an image
				\item good lens can increase sharpness and therefore stitching accuracy and ML inference
				\item obtain similar quality between the corner and center of the image
				\item Difficulty stitching with lower detail images, can't increase digitizing speed, must downscale high resolution images 
		\item poor lens quality seemed to be the culprit of producing visible seams when stitching with larger field of view images 
	\item tested on R-CNN
		\item Cookie with a dpi of SMALL and dpi of 13500 were tested. With total pixel count of SMALL and BIG
			\item NEEDS specific: DPI, height and width of pixels, record runtime
			\item NEEDS specifications of server computational power (GPU count/other metric for ANN power)
	\item tested on CooRecorder + CDendro
		\item Maximum filesize 
		\item Coordinates were registered on to the cookie scans 
		\item Note to self: using CDendro for multiple samples from the same tree... (cookies) 
	\item Software support for large files 
		\item Not all software can support this, especially if the computer is RAM constrained. Ring analysis tool which uses BigTIFF, HD5, or memory maps and loads only partial portions of the full image would be useful
\item Conclusions (optional for MEE) % Usually I am anti-conclusions because you just end up repeating yourself, but I think this could work here, especially to end on a positive after the 'opportunities' section. I think you could add  the 'potential for automatic tree ring identification with iamge processing / ML ' and 'potential for vessel counts for an entire ring'  here perhaps.
	\item empty
